Shifting mutational effects on the evolutionary landscape of HIV Envelope

### 2017-11-12 paper/manuscript.tex
resized panel C in `omegabysite_structural_analysis` figure
start work on prefs dist

\begin{figure}
\begin{fullwidth}
{\includegraphics[width=1.3\textwidth]{figures/BG505_prefs.pdf}}
\caption{\label{fig:bg505_prefs_logo}
The rescaled averaged site-specific amino-acid preferences for BG505.
This logo plot shows the site-specific amino-acid preferences for BG505 after averaging between replicates and then rescaling them using the stringency parameter from Table \ref{tab:phydms} inferred for BG505 from the group-M alignment.
Each site has a stack of 20 letters corresponding to the 20 amino acids.
Letter heights, which sum to one at each site, are proportional to the site's preference for each amino acid.
The top bar (R) indicates gp120 variable loops, other regions in gp120, or gp41.
The bottom bar (WT) shows the wildtype amino-acid sequence for BG505.
Sites are numbered according to the HXB2 numbering scheme~\cite{korber1998numbering}).
}
\figdata{The re-scaled preferences plotted in this figure are in \texttt{rescaled\_BG505\_prefs.csv.}}
\figdata{Sequence of the BG505 Env and mapping from sequential 1, 2, ... numbering of this sequence (\emph{original} column) to HXB2 numbering (\emph{new} column) is in \texttt{BG505\_to\_HXB2.csv}.}
\figdata{The $\omega_r$ values and associated $P$-values for BG505 in HXB2 numbering are in \texttt{BG505\_omegabysite.tsv}.}
\end{fullwidth}
\end{figure}
\FloatBarrier

@@

\begin{figure}
%\includegraphics[width=0.5\textwidth]{figures/diversifying_selection_corr.pdf}
\includegraphics[width=1.0\textwidth]{figures/omegabysite_structural_analysis/omegabysite_structural_analysis.pdf}
\caption{\label{fig:divselcorr}
Correlation between sites of diversifying and purifying selection among homologs.
\jdbcomment{Hugh - can you make the panel showing the relationship between purifying selection and the Andrew Ward sites.}  
}
\figsupp[Amino-acid preferences and alignment frequencies at sites of purifying selection.]{
This plot shows all sites that are evolving more slowly than expected in natural sequences given the preferences measured in both homologs.
Specifically, it shows all sites with $\omega_r < 1$ at $Q < 0.05$ for the ExpCMs for \emph{both} BG505 and BF520.
For each site, the plots show the preferences averaged across replicates and re-scaled for each homolog, as well as the frequencies of amino acids in the clade A Env alignment. 
The $Q$-value indicated is the maximum of that for the two homologs.
}{\includegraphics[width=\textwidth]{figures/purifying_selsites.pdf}}
\figsupp[Distribution of relative solvent accessibilities among sites of diversifying and purifying selection.]{
Sites are grouped by whether they are under diversifying or purifying selection at $Q < 0.05$ in \emph{both} homologs, or whether they do not fall into either of these categories.
The absolute solvent accessibility of each site in the BG505 SOSIP trimer in PDB 5FYL~\citep{?} was calculated using DSSP~\citep{?}, and normalized to a relative solvent accessibility using the absolute accessibilities provided by \citet{?}.
As can be seen from these box plots with overlaid points for each site, sites of both diversifying and purifying selection tend to have higher relative solvent accessibility than other sites.
}{\includegraphics[width=0.5\textwidth]{figures/selsites_rsa.pdf}}
\figdata{The $\omega_r$ and associated $P$-values plotted in this figure are in \texttt{merged\_omegabysite.csv}.}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}
\begin{fullwidth}
{\includegraphics[width=1.3\textwidth]{figures/BG505_prefs.pdf}}
\caption{\label{fig:bg505_prefs_logo}
The rescaled averaged site-specific amino-acid preferences for BG505.
This logo plot shows the site-specific amino-acid preferences for BG505 after averaging between replicates and then rescaling them using the stringency parameter from Table \ref{tab:phydms} inferred for BG505 from the group-M alignment.
Each site has a stack of 20 letters corresponding to the 20 amino acids.
Letter heights, which sum to one at each site, are proportional to the site's preference for each amino acid.
The top bar (R) indicates gp120 variable loops, other regions in gp120, or gp41.
The bottom bar (WT) shows the wildtype amino-acid sequence for BG505.
Sites are numbered according to the HXB2 numbering scheme~\cite{korber1998numbering}).
}
\figdata{The re-scaled preferences plotted in this figure are in \texttt{rescaled\_BG505\_prefs.csv.}}
\figdata{Sequence of the BG505 Env and mapping from sequential 1, 2, ... numbering of this sequence (\emph{original} column) to HXB2 numbering (\emph{new} column) is in \texttt{BG505\_to\_HXB2.csv}.}
\figdata{The $\omega_r$ values and associated $Q$-values for BG505 in HXB2 numbering are in \texttt{BG505\_omegabysite.tsv}.}
\end{fullwidth}
\end{figure}
\FloatBarrier

@@

\begin{figure}
%\includegraphics[width=0.5\textwidth]{figures/diversifying_selection_corr.pdf}
\includegraphics[width=1.0\textwidth]{figures/omegabysite_structural_analysis/omegabysite_structural_analysis.pdf}
\caption{\label{fig:divselcorr}
Correlation between sites of diversifying and purifying selection among homologs.
}
\figsupp[Amino-acid preferences and alignment frequencies at sites of purifying selection.]{
This plot shows all sites that are evolving more slowly than expected in natural sequences given the preferences measured in both homologs.
Specifically, it shows all sites with $\omega_r < 1$ at $Q < 0.05$ for the ExpCMs for \emph{both} BG505 and BF520.
For each site, the plots show the preferences averaged across replicates and re-scaled for each homolog, as well as the frequencies of amino acids in the clade A Env alignment. 
The $Q$-value indicated is the maximum of that for the two homologs.
}{\includegraphics[width=\textwidth]{figures/purifying_selsites.pdf}}
\figsupp[Distribution of relative solvent accessibilities among sites of diversifying and purifying selection.]{
Sites are grouped by whether they are under diversifying or purifying selection at $Q < 0.05$ in \emph{both} homologs, or whether they do not fall into either of these categories.
The absolute solvent accessibility of each site in the BG505 SOSIP trimer in PDB 5FYL~\citep{?} was calculated using DSSP~\citep{?}, and normalized to a relative solvent accessibility using the absolute accessibilities provided by \citet{?}.
As can be seen from these box plots with overlaid points for each site, sites of both diversifying and purifying selection tend to have higher relative solvent accessibility than other sites.
}{\includegraphics[width=0.5\textwidth]{figures/selsites_rsa.pdf}}
\figdata{The $\omega_r$ and associated $P$-values plotted in this figure are in \texttt{merged\_omegabysite.csv}.}
\end{figure}
\FloatBarrier
